### 2014-10-01 tex/proofs.tex
Added commentary

If the $\varsigma$-relation is considered to be a model of the
$\ell-relation$ (i.e., a representation of that machine), then the
representation relation, as a bisimulation, ensures that the
$\varsigma$-relation is complete in that it any property that can be
shown in the $\ell$-relation can also be shown in the
$\varsigma$-relation; and further, the representation relation as a
bisimulation ensures that the $\varsigma$-relation is also sound in
that any property that can be shown to hold in the $\varsigma$-relation
can also be shown to hold in the $\ell$-relation.

The proof of the representation relation as a bisimulation reasons
over individual rules in the $\varsigma$-relation to show that each
rule preserves exactness. That is to say that whenever the state on
the left of the $\varsigma$-relation has a corresponding state that it
represents in the $\ell$-relation, its successor set is both sound and
complete relative the $\ell$-relation and subject to the
representation relation. Intuitively, the $\varsigma$-relation, at a
given state, has a successor to account for every successor from the
$\ell$-relation at the corresponding state, and the $ell$-machine has
a successor to account for every successor in the
$\varsigma$-relation.

The proof of exactness of each rule relies on the ability to derive
from the homomorphism in the representation relation in the current
state, a new homomorphism that is sufficient to use in the
representation relation that reasons over the successor states. The
proof is constructive in that it shows how given a valid homomorphism
for the current state, it is possible to derive a new homomorphism to
reason about successor states.

@@

The equals-reference proof must show that any given reference in the
heap is not able to point to two distinct locations at the same
time. If the incoming heap is able to point to two valid locations at
a given reference at the same time, then the help is
non-deterministic, and it is not possible to construct a valid
homomorphism from the existing homomorphism: which location should be
used in the map? As such, the proof first establishes that
$\varsigma$-relation preserves location mutual exclusive in the
incoming heap. Once that is shown, the exactness of the equals
reference rule is given.

>>>>

If the $\varsigma$-relation is considered to be a model of the
$\ell$-relation (i.e., a representation of that machine), then the
representation relation, as a bisimulation, ensures that the
$\varsigma$-relation is complete in that any property that can be
shown in the $\ell$-relation can also be shown in the
$\varsigma$-relation; and further, the representation relation as a
bisimulation ensures that the $\varsigma$-relation is also sound in
that any property that can be shown to hold in the $\varsigma$-relation
can also be shown to hold in the $\ell$-relation.

The proof of the representation relation as a bisimulation reasons
over individual rules in the $\varsigma$-relation to show that each
rule preserves exactness. That is to say that whenever the state on
the left of the $\varsigma$-relation has a corresponding state that it
represents in the $\ell$-relation, its successor set is both sound and
complete relative the $\ell$-relation and subject to the
representation relation. Intuitively, the $\varsigma$-relation, at a
given state, has a successor to account for every successor from the
$\ell$-relation at the corresponding state, and the $\ell$-machine has
a successor to account for every successor in the
$\varsigma$-relation.

The proof of exactness of each rule relies on the ability to derive
from the homomorphism in the representation relation in the current
state, a new homomorphism that is sufficient to use in the
representation relation that includes the successor states. The proof
is constructive in that it shows how given a valid homomorphism for
the current state, it is possible to derive a new homomorphism that
includes successor states.

@@

The equals-reference proof must show that any given reference in the
heap is not able to point to two distinct locations at the same
time. If the incoming heap is able to point to two valid locations at
a given reference at the same time, then the help is
non-deterministic, and it is not possible to construct a valid
homomorphism from the existing homomorphism: which location should be
used in the map? As such, the proof first establishes that
the $\varsigma$-relation preserves location mutual exclusive in the
incoming heap. Once that is shown, the exactness of the equals
reference rule is given.
